---
title: "Pitch Presentation"
author: "Arthur LAUREAU - Igor FIDALGO"
date: "November 26, 2019"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 1. Introduction

### **The Shiny Application project**:

This project is a simple hello world project to learn how to make a **Shiny app** and a related **presentation** using **RStudio**.
To learn more, see [our github](https://github.com/Igzs/R_shiny_pres).  

## 2. Dataset summary

The **UCBAdmissions** data set is frequently used for illustrating **Simpson's paradox**, see [Bickel et al (1975)](http://www.jstor.org/stable/1739581). At issue is whether the data show evidence of sex bias in admission practices.  

To learn more, see Data from Berkeley. Science, 187, 398--403.

The UCBAdmissions data set is 3-dimensional array resulting from cross-tabulating 4526 observations on 3 variables. The variables and their levels are as follows: 

| No   |  Name  |       Levels       |
|:----:|:------:|:------------------:|
|   1  |  Admit | Admitted, Rejected |
|   2  | Gender |    Male, Female    |
|   2  |  Dept  |     A,B,C,D,E,F    |
  
  
```{r UCBAdmissions}
summary(UCBAdmissions)
```

## 3. Functionalities

- Plot graphs
- Is cool
- Made with love

## 4. Interactive Plot

```{r eruptions}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```